\sys: Light-touch Data-Parallel Shell Processing

### 2020-10-07 paper/draft.tex
Update pipelines in Unix50

%% \TODO{An important point that needs to be made clear is that these are
%%   taken from the wild unmodified. And that Pash never leads to
%%   slowdown (except for the trivial head cases, where the slowdown is
%%   neligible).}
\heading{Results}
\sys's parallelism is set to $16\times$, as many of these pipelines are relatively long (\S\ref{ours}, Discussion).
Their input was generated by multiplying their original input several times, enough to reach 10GB.
Fig.~\ref{fig:unix50-individual} shows the speedup (left) over the sequential runtime (right) for all 34 pipelines. We use the pipeline index to refer to them in both plots and discussion.
%% (\nv{Pipelines are referred by number, in both the plot and the discussion below.})
Average speedup is \todo{$5.49\times$}, median is $6.07\times$, and weighted average (with the absolute times as weights) is $5.75\times$.
 % the \todo{geometric mean is $1.08\times$},
\kk{We don't include three pipelines that took less than 0.1 seconds to execute because they only modified the first line of their input using \ttt{head}}

%% Mean: 5.499164686559543
%% Median: 6.075774436154179
%% Geometric Mean: 1.0798740409683736
%% Weighted Average: 5.752406752503295

\heading{Discussion}
Most pipelines see significant acceleration, except \todo{13, 24, 25, 26, 29, 30} that see no speedup and \todo{2, 19, 31} that see a slowdown.
The first group contains commands which \sys cannot parallelize without risking breakage---\eg \ttt{awk} and \ttt{sed} \ttt{-d}. % and \ttt{tr} \ttt{-d}.
Note however, that some of the pipelines contain more general commands that cannot be parallelized since they were not written with that goal in mind; a common example is the use of \ttt{awk} for reordering or removing columns of the input.
%% Some of them use general interpreters when they could be using a specialized equivalent tailored to the task at hand, the typical example being \ttt{awk} vs \ttt{cut}.
In particular, replacing an \ttt{awk} that was just used to sort on the second field \ttt{awk "{print \$2, \$0}" | sort -nr} with a single \ttt{sort -nr -k 2} in the \todo{13th} pipeline allows \sys to achieve 8.1$\times$ speedup (in contrast to the original 1.01$\times$).
%% , attempting only such obvious (to us, experts) replacements, \sys extracts further parallelism---\eg 13 sees a 8.1$\times$ speedup.
% ---a common pattern we witnessed~\sx{macro1}.

The second group contains \ttt{head}, thus practically processing only one line (regardless of the full input) and completing within $10ms$.
\sys's slowdown is due to constant setup costs of pipes and processes but execution still remains under $1s$.

@@

For the rest, \sys's speedup is capped due to a combination of reasons:
  (i) they contain pure commands that are parallelizable but don't scale linearly, such as \ttt{sort} \todo{(0, 1, 3, 15, 16, 18, 20, 27, 28, 33)},
  (ii) some are deep pipelines that already exploit task-based parallelism \todo{(7, 8, 9, 10, 11, 12, 14, 27, 28,)} and
  (iii) they are not CPU-intensive, resulting in pronounced IO and constant costs \todo{(4, 5, 6, 7, 8, 12, 14, 22, 23)}.

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{\detokenize{./figs/unix50_individual_speedups_16.pdf}}
  \caption{
	  \textbf{Unix50 scripts.}
    Speedup (left axis) over sequential execution (right axis) for Unix50 scripts.
    Parallelism is 16$\times$ on 10GB of input data~\cf{unix50}.
    \todo{Pipelines are sorted in descending speedup order.} 
    % The solid line indicates the average speedup $\times5.49$ and the dotted line indicates 1.
    % \nv{Idea: scripts that only take over 0.01s?}
    % \kk{Now that we removed the small ones, sequential time does not add a lot to this plot. Maybe we can just show speedups?}
  }
  \vspace{-15pt}
  \label{fig:unix50-individual}
\end{figure}

>>>>

%% \TODO{An important point that needs to be made clear is that these are
%%   taken from the wild unmodified. And that Pash never leads to
%%   slowdown (except for the trivial head cases, where the slowdown is
%%   neligible).}
\heading{Results}
\sys's parallelism is set to $16\times$, as many of these pipelines are relatively long (\S\ref{eval}, Parallelism).
Their input was generated by multiplying their original input several times, enough to reach 10GB.
Fig.~\ref{fig:unix50-individual} shows the speedup (left) over the sequential runtime (right) for all 34 pipelines. We use the pipeline index to refer to them in both plots and discussion.
%% (\nv{Pipelines are referred by number, in both the plot and the discussion below.})
Average speedup is \todo{$6.02\times$}, median is $6.48\times$, and weighted average (with the absolute times as weights) is $5.75\times$.
 % the \todo{geometric mean is $1.08\times$},
We do not include three pipelines that take less than 0.1 seconds to execute because they only output the first line of their input using \ttt{head}.

  % Mean: 6.028795730618471
  % Median: 6.48837000168888
  % Geometric Mean: 4.765602271688225
  % Weighted Average: 5.752417060139914

\heading{Discussion}
Most pipelines see significant acceleration, except 25-30
  % \todo{13, 24, 25, 26, 29, 30} 
  that see no speedup. 
  % and \todo{2, 19, 31} that see a slowdown.
These pipelines contain commands which \sys cannot parallelize without risking breakage---\eg \ttt{awk} and \ttt{sed} \ttt{-d}. % and \ttt{tr} \ttt{-d}.
Note however, that some of the pipelines contain more general commands that cannot be parallelized since they were not written with that goal in mind; a common example is the use of \ttt{awk} for reordering or removing columns of the input.
%% Some of them use general interpreters when they could be using a specialized equivalent tailored to the task at hand, the typical example being \ttt{awk} vs \ttt{cut}.
In particular, replacing an \ttt{awk} that was just used to sort on the second field \ttt{awk "{print \$2, \$0}" | sort -nr} with a single \ttt{sort -nr -k 2} in the 
  % \todo{13th} 
  26th pipeline allows \sys to achieve 8.1$\times$ speedup (in contrast to the original 1.01$\times$).
%% , attempting only such obvious (to us, experts) replacements, \sys extracts further parallelism---\eg 13 sees a 8.1$\times$ speedup.
% ---a common pattern we witnessed~\sx{macro1}.

% The second group contains \ttt{head}, thus practically processing only one line (regardless of the full input) and completing within $10ms$. 
% \sys's slowdown is due to constant setup costs of pipes and processes but execution still remains under $1s$.

@@

For the rest, \sys's speedup is capped due to a combination of reasons:
  (i) they contain pure commands that are parallelizable but don't scale linearly, such as \ttt{sort} 
  5, 6, 7, 8, 9, 19, 20, 21, 23, 24,
  % 24, 9, 7, 6, 8, 23, 20, 19, 21, 5
  % \todo{(0, 1, 3, 15, 16, 18, 20, 27, 28, 33)},
  (ii) some are deep pipelines that already exploit task-based parallelism 
  4, 10, 11, 13, 15, 17, 19, 21, 22,
  % 17, 4, 13, 15, 10, 22, 11, 19, 21,
  % \todo{(7, 8, 9, 10, 11, 12, 14, 27, 28,)} 
  and
  (iii) they are not CPU-intensive, resulting in pronounced IO and constant costs 
  3, 4, 11, 12, 14, 16, 17, 18, 22.
  % 14, 3, 16, 17, 4, 22, 11, 12, 18
  % \todo{(4, 5, 6, 7, 8, 12, 14, 22, 23)}.

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{\detokenize{./figs/unix50_individual_speedups_16.pdf}}
  \caption{
	  \textbf{Unix50 scripts.}
    Speedup (left axis) over sequential execution (right axis) for Unix50 scripts.
    Parallelism is 16$\times$ on 10GB of input data~\cf{unix50}.
    Pipelines are sorted in descending speedup order. 
    % The solid line indicates the average speedup $\times5.49$ and the dotted line indicates 1.
    % \nv{Idea: scripts that only take over 0.01s?}
    % \kk{Now that we removed the small ones, sequential time does not add a lot to this plot. Maybe we can just show speedups?}
  }
  \vspace{-15pt}
  \label{fig:unix50-individual}
\end{figure}
